Verifying Demonstrations

### 2018-02-28 paper/protocol.tex
Updates protocol, changes \PRF to \ACprf

\begin{figure*}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets \PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon &
        \DBPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}] \\
      W\colon & wid\gets \PRF_{k_W}(pid), \\
        & wsig\gets \PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig, \pi_W),\quad \text{where}\\
        & \pi_W = \SPK[k_W, \sigma_W]%
          [wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
            \Sign[k]{k_W}][pid, wid, t_s, l, wsig] \\
      P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
        & \pi_P = \SPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = 
          \Sign[k]{k_P}][pid, wid, t_s, l, wsig]
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure*}

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, \eg by 
  \citet{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets \PRF_k(cid)\), which is her anonymous 
identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).

@@

Alice must provide \iac{NIZK} proof showing that \(pid = \PRF_{k_P}(cid)\) and 
that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]

In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
  \PRF_{k_W}(pid)\) and \(wsig = \PRF_{k_W}(wid, t_s, l)\) as well as that the 
witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
eligibility, of the proof shares and thus also count them.

@@

More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
must remove her secret \ac{PRF} key, \(k_A\).
With this key Eve can verify that Alice has submitted a proof by computing 
\(pid'\gets \PRF_{k_A}(cid)\) and compare \(pid = pid'\).

>>>>

\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
      W\colon & t_s'\gets \TSget \\
      P\colon & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{k_P}][cid]
      & \text{\small Join} \\ \midrule && \text{\small Participation} \\[-1.5em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s, t_s', l, wsig)
      & \text{\small Participation} \\ \midrule && \text{\small Submission} 
      \\[-1.5em]
      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
      \text{where} \\
        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
        & \qquad wid = \ACprf[_{k_W}][pid], \\
        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
      \text{where}\\
        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO\@.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, \eg by 
  \citet{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets \ACprf[_k][cid]\), which is her 
anonymous identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).

@@

Alice must provide \iac{NIZK} proof showing that \(pid = \ACprf[_{k_P}][cid]\) 
and that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]

In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
  \ACprf[_{k_W}][pid]\) and \(wsig = \ACprf[_{k_W}][wid, t_s, l]\) as well as 
that the witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
eligibility, of the proof shares and thus also count them.

@@

More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
must remove her secret \ac{PRF} key, \(k_A\).
With this key Eve can verify that Alice has submitted a proof by computing 
\(pid'\gets \ACprf[_{k_A}][cid]\) and compare \(pid = pid'\).
